%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Florida Atlantic University, Department of Electrical Engineering and Computer Science} % Job title
{\textbf{Graduate Student Researcher}} % Organization
{Boca Raton, FL} % Location
{Aug. 2018 - Aug. 2022} % Date(s)
{Autonomous Systems such as Robotic Swarm are required to communicate on a secured protocols to achieve an agreement of operation. The following algorithms were developed as part of the research that explores how autonomous systems can use consensus algorithms to improve operation and achieve an agreement on a set of rules on dynamic environments.
\newline[0.5\baselineskip]
\textit{Autonomous Units Consensus Algorithm}
\begin{itemize}
	\item {Created a consensus algorithm designed to be implemented in autonomous systems that can verify the communicative data over a malicious environment}
	\item {Included trust value and digital signature among other cryptographic primitives to achieve a secured information sharing protocol}
	\item {Implemented using RPC written in C and Python. Simulated with ARGoS simulator}
\end{itemize}~\newline
\textit{Localized State-Change Consensus Algorithm}
\begin{itemize}
	\item {Created An algorithm designed to achieve consensus with validation of dynamic environmental data through reputation value. Assures confidentiality, integrity and validity of messages on the blockchain among all users}
	\item{Implemented as a sub-ledger on the Hyperledger framework and then analyzed to ensure efficiency, scalability and security}
	\item {Maintained good source documentation following good documentation practices}
\end{itemize}~\newline
\textit{Security Improvements of Blockchain Architecture}
\begin{itemize}
	\item {Reviewed and analyzing a large number of known and less-known attacks on consensus algorithms and blockchain architecture}
	\item {Built a simulated environment using ARGoS that handles malicious nodes}
\end{itemize}
}


%------------------------------------------------    

\cventry
{Florida Atlantic University, Department of Electrical Engineering and Computer Science} % Job title
{\textbf{Teaching Assistant}} % Organization
{Boca Raton, FL} % Location
{May. 2022 - Aug. 2022} % Date(s)
{\begin{cvitems}
		\item Teaching assistant for Data Structure and Algorithm Analysis: led discussion hours (~50 students), held office hours
	\end{cvitems}
}

%------------------------------------------------    

\cventry
{Telit IoT Platforms} % Job title
{\textbf{Software Engineering Intern}} % Organization
{Boca Raton, FL} % Location
{Jul. 2017 - Jan. 2020} % Date(s)
{\begin{cvitems}
		\item Supported development and QA for driver development
		\item Developed projects in C while contributing to deployment by testing, debugging, and resolving issues for optimal results
		\item Consulted with engineering staff to evaluate interface between hardware and software to develop specifications and performance requirements or resolve customer problems
\end{cvitems}
}

%------------------------------------------------    

\cventry
{IAF, International Aviation} % Job title
{\textbf{Special Operations Specialist}} % Organization
{Be'er Sheva, Israel} % Location
{Aug. 2013 - Jul. 2016} % Date(s)
{\begin{cvitems}
		\item Led team focused on analyzing and deploying new technology in aviation strategic capabilities
		\item Implemented complex scenarios of operation as a training platform in hostile environment
	\end{cvitems}
}


\end{cventries}